---
title: "Financial data Analysis"
autor: "Murtiza"
date: last-modified
toc: true
format: 
  html: default
  pdf: default
---

## Introduction

Analyzing Johnson & Johnson's quarterly earnings data from 1960 to 1980 offers a comprehensive understanding of the company's financial performance, facilitates investment decision-making, and provides insights into its strategic management and competitive position in the market.

## Research Questions

1.  asdfasfasf
2.  sdafasdfas
3.  dfasddfasdfas

```{r libraries, message=FALSE, warning=FALSE, echo=FALSE}

library(datasets)
library(ggplot2)
library(dplyr)
library(tsbox)
library(knitr)
```

## Data-set Introduction

Johnson & Johnson's quarterly earnings data from 1960 to 1980.

Link: [https://quarto.org/docs/output-formats/html-multi-format.htmlhttps://quarto.org/docs/output-formats/html-multi-format.html](https://quarto.org/docs/output-formats/html-multi-format.html)

```{r dataset_intro, warning=F, message=F}

mydata <- datasets::JohnsonJohnson
mydata <- ts_df(mydata)


variables<- colnames(mydata)
explanations <- c("Quarterly date from 1960  to 1980",
                  "Earnings in dollar (milllion)")
var_expl<- data_frame(variables,explanations )

kable(var_expl)



```

### Dataset details

```{r details}




```
